Deep Learning for Automatic Speech Recognition

### 2015-04-22 Presentation/Presentation.tex
Finalized slides

	\begin{itemize}
		\item Convert the spectrum of a window into its cepstrum
		\item Effectively separates the source from filter
		\item Cepstral coefficients are uncorrelated
		\item Use the first 12 (represent the filter), their deltas and delta-deltas for 39 features per frame
	\end{itemize}

@@

\begin{frame}
	\frametitle{Gaussian Mixture Models}\TODO{clean up}
	\begin{center}
		\includegraphics[scale=.3, clip=true, trim=5cm 9cm 4cm 10cm]{gmm.pdf}
	\end{center}

	\begin{center}
		Before the rise of Deep Learning approaches, GMMs were ubiquitous for representing the acoustic model.
	\end{center}
	\begin{center}
		Based on assumption that a mixture of Gaussians can be used to represent the spectral shape.
	\end{center}

@@

	\begin{center}
	Below is the output likelihood function $b_{j}(o_{t})$:
	\end{center}

	\begin{equation*}
	b_{j}(o_{t}) = \sum_{m=1}^{M}c_{jm}\frac{1}{\sqrt{2\pi|\sigma_{jm}|}}\exp[(x-\mu_{jm})^T\sigma_{jm}^{-1}(o_{t}-\mu_{jm})]
	\end{equation*}

	\begin{center}
		A GMM model can be trained using the Baum-Welch algorithm to iteratively recompute the mean, mixture weight, and covariance.
	\end{center}

>>>>

	\begin{itemize}
		\item Convert the spectrum of a window into its cepstrum
		\item Effectively separates the source from filter
		\item Cepstral coefficients are uncorrelated
		\item Use first 12 (represent the filter) and an energy coefficient, their deltas and delta-deltas for 39 features per frame
	\end{itemize}

@@

\begin{frame}
	\frametitle{Gaussian Mixture Models}
	\begin{center}
		\includegraphics[scale=.25, clip=true, trim=0cm 5.5cm 0cm 5cm]{gmm.pdf}
	\end{center}

	\begin{center}
		Before rise of Deep Learning approaches, GMMs were ubiquitous for representing the acoustic model.
	\end{center}
	\begin{center}
		Based on assumption that a mixture of Gaussians can be used to represent the spectral shape of a phone or sub-phone.
	\end{center}	
	\begin{center}
		\tiny{Credit: Wikipedia}
	\end{center}
\end{frame}

@@

	\begin{center}
	Below is the output likelihood function $b_{j}(o_{t})$:

	\begin{equation*}
	b_{j}(o_{t}) = \sum_{m=1}^{M}c_{jm}\frac{1}{\sqrt{2\pi|\sigma_{jm}|}}\exp[(x-\mu_{jm})^T\sigma_{jm}^{-1}(o_{t}-\mu_{jm})]
	\end{equation*}
	\end{center}
	\begin{center}
		A GMM model can be trained using the Baum-Welch algorithm to iteratively recompute the mean, mixture weight, and covariance.
	\end{center}
